---
title: "hw6-sx2267"
author: "ShibeiXu"
date: "2021/12/4"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = F, 
                      warning = F, 
                      out.width = "90%")
library(tidyverse)
library(leaps)
library(patchwork)
theme_set(theme_bw())
```

## Problem 1
```{r}
data1 = read.csv("birthweight.csv")%>% 
  as.tibble() %>% 
  janitor::clean_names()
```

```{r cleaning and factorize the dataset}
data1 =
  data1 %>% 
  mutate(babysex = factor(babysex),
         malform = factor(malform),
         mrace = factor(mrace, levels = c(1, 2, 3, 4, 8)))
```

```{r checking missing value }
summary(data1)
#we see there is all 0s in multiple variables
data1 =
  data1 %>% 
  select(-pnumlbw, -pnumsga)
```

```{r use backward stepwise}
lm(bwt ~ ., data = data1) %>% 
  step(direction='backward')
```
Based on the stepwise model, the final model are: babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken

```{r residual plot}
model1 = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = data1)
data1 %>% 
  modelr::add_predictions(model1) %>% 
  modelr::add_residuals(model1) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(aes(alpha = 0.5)) +
  theme(legend.position = "none")
```

```{r compare 2 models}
compare_df1 = 
  modelr::crossv_mc(data1, 500) %>% 
  mutate(train = map(train, as.tibble), 
         test = map(test, as.tibble)) %>% 
  mutate(model1 = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)), 
         test1_mod = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)), 
         test2_mod = map(train, ~lm(bwt ~ bhead+blength+babysex+bhead * blength * babysex, data = .x))) %>% 
  mutate(rmse_optimal = map2_dbl(model1, test, ~modelr::rmse(model = .x, data = .y)), 
         rmse_test1 = map2_dbl(test1_mod, test, ~modelr::rmse(model = .x, data = .y)),
         rmse_test2 = map2_dbl(test2_mod, test, ~modelr::rmse(model = .x, data = .y)))
```

```{r}
compare_df1 %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```
The optimal model has the highest prediction accuracy.

## Problem 2

```{r load the data}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
```{r}
head(weather_df,10)
summary(weather_df)
```
```{r create boot function}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}
```

```{r conduct bootstrap of 5000}
boot_strap = 
  data_frame(
    strap_number = 1:5000,
    strap_sample = rerun(5000, boot_sample(weather_df))
  )
bootstrap_result = 
  boot_strap %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap_sample, -models) %>% 
  unnest(results) 
```

```{r R^2 analysis}
bootstrap_result %>%
  ggplot(aes(x = adj.r.squared)) + 
  geom_density()
```

The CI of adjusted R square is `r quantile(bootstrap_result$adj.r.squared, probs=0.025)` , `r quantile(bootstrap_result$adj.r.squared, probs=0.975)`

```{r for log betas functions}
log_beta_p = function(df) {
    log(df[1,2]*df[2,2]) %>% 
    tibble() %>% 
    mutate(
      log_betas=.$estimate) %>% 
    select(log_betas)
}
```


```{r}
bootstrap_result_1=
  boot_strap %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy),
    log_betas = map(results, log_beta_p)) %>% 
  select(-strap_sample, -models) %>%
  unnest(log_betas)
```

```{r density plot}
bootstrap_result_1%>%
  ggplot(aes(x = log_betas)) + 
  geom_density()
```
The density plot indicates a normal distribution with mean centered around 2-2.05
The CI of adjusted R square is `r quantile(bootstrap_result_1$log_betas, probs=0.025)` , `r quantile(bootstrap_result_1$log_betas, probs=0.975)`


